A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-16 papers/paper1/ms.tex
Working on pdf

\usepackage[caption=false]{subfig}
\usepackage{censor}
\usepackage{booktabs}

@@

@@

>>>>

\usepackage[caption=false]{subfig}
\usepackage{censor}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage[section]{placeins}
\graphicspath{{./figures/}}

@@

We compared the amplitudes of the TESS and Kepler spacecraft using the rapid rotator sample. As seen below, we developed a mask that eliminates outliers that beyond predefined boundaries. We decide to discard any points that exceed 80\% of the perfect correlation and points with over a 7 days period. The first requirement was decided because anything that differs by more than 80\%, in our opinion, most certainly the result of data fluctuations. Similarly, due to measurement errors, we have to exclude any periods longer than 7 days. The TESS mission only captured around 22 days worth of data for each object. We wanted to have at least 3 periods for each object.

  % Helpful resource on how to insert and align images
  % https://www.overleaf.com/learn/latex/Inserting_Images
  \begin{figure}[!htb]
    \centering
    \includegraphics[scale=0.8]{Comparison Between TESS and Kepler Amplitudes.png}
    \caption{Relationship between the calculated amplitudes of TESS and Kepler and how close they are to unity}
  \end{figure}
  \FloatBarrier

@@

 As seen in the figure below, the Kepler data are, on average, around 70 times larger than TESS's.

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{Amplitude vs. Rotation for Kepler and TESS.png}
    \caption{Comparison between the rotational period vs. amplitude for both TESS and Kepler. The Kepler and TESS averages are approximately 9350 and 130, respectively}
  \end{figure}
  \FloatBarrier
